Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-07-15 manuscript.tex
Initial work on random data

\subsection*{Absence of information is correctly handled by nSBM}

@@

This experiment is a deliberate extreme case. The quality of grouping proposed by a standard approach can be disputed in many ways, and the UMAP embedding indeed reflects the absence of any information. Nevertheless, real-world data may include an unknown amount of random noise. Hence, It is important to identify cell groups that are not artefacts arising from processing and that do reflect the information contained in the dataset.

>>>>

\subsection*{\texttt{schist} is robust to data perturbation}

@@

This experiment is a deliberate extreme case. The quality of grouping proposed by a standard approach can be disputed in many ways, and the UMAP embedding indeed reflects the absence of any information. Nevertheless, real-world data may include an unknown amount of random noise. Hence, It is important to identify cell groups that are not artefacts arising from processing and that do reflect the information contained in the dataset. \textcolor{red}{To understand the impact of random noise on structured data, we considered the same dataset and added gaussian noise to the normalised counts at increasing levels of $\sigma$, ensuring that the noise level is modeled after the feature-wise distribution of expressed genes (\emph{e.g.} genes with counts higher than zero). We noticed that \texttt{schist} is more robust to perturbations, although none of the methods can be considered reliable when $\sigma \geq 1.5$ (Table \ref{Table_Noise}.}
